---
title: "Use cases for comcomcol"
author: "Frederik Sachser"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
library(datawoman)
```

# Example 1:
- check classes and frequency of slightly different dataframes before conducting a merge/join/combine
```{r}
df1 <- df2 <- df3 <- df4 <- iris[1:4]
df1$Petal.Width <- as.character(df1$Sepal.Width)
df2$Sepal.Width <- NULL
df3 <- df4[1:5,]
comcomcol(df1, df2, df3, df4)
```

# Example 2
- compare consistency of mean for all numeric variables of iris data by increasing sample size
```{r}
df1 <- df2 <- df3 <- df4 <- iris[1:4]
n <- 1:nrow(iris)
df1 <- df1[sample(n, 10),]
df2 <- df2[sample(n, 50),]
df3 <- df3[sample(n, 100),]
comcomcol(df1, df2, df3, df4, custom_fun = mean)
```

# Example 4:
- Specify your own function for comparison
```{r}
df1 <- df2 <- df3 <- df4 <- mtcars
df3$mpg <- NULL
df2$hp <- NULL
comcomcol(df1, df2, df3, df4, custom_fun = function(x) round(median(x^3)))
```

# Example 4
-  Quickly check the classes of your dataframe with a clean look.
```{r}
comcomcol(iris)
```

# Example 5
- Quickly check mean (or any other function) of all possible columns of your dataframe. Warning message appears in case of impossible call (e.g. mean of a character variable). Even if your custom function will fail in some cases all other columns will behave as expected.
```{r}
comcomcol(iris, custom_fun = mean)
```
